### 2018-01-14 paper.tex
Added programming historian citation (again happy to be rolled back!)

The authors have many years of experience with community-developed lessons
in the context of research computing in the sciences and humanities,
through organizations like Software Carpentry (\url{https://software-carpentry.org/}) and Programming Historian (\url{https://programminghistorian.org/}).
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanities scholars.
Their guiding principles are that lessons should be:

@@

>>>>

The authors have many years of experience with community-developed lessons
in the context of research computing in the sciences and humanities,
through organizations like Software Carpentry and Programming Historian \cite{proghist}.
Software Carpentry was founded in 1998 to teach scientists basic computing skills,
and has since spawned two sibling organizations called Data Carpentry and Library Carpentry.
Programming Historian was founded in 2008,
and has evolved into a collaboratively-edited site providing lessons to humanities scholars.
Their guiding principles are that lessons should be:

@@

\bibitem{proghist}
Afanador-Llach MJ, Baker J, Crymble A, Gayol V, Gibbs F, Lincoln M, McDaniel C, Milligan I, Parr J, Castro AR, Knuppel AS, Visconti A, Walsh B, Wieringa J.
\newblock Programming Historian,
\newblock \url{https://programminghistorian.org/}.
